### 2010-03-31 papers/icfp-2010-desc/paper_idesc.tex
Desc@ICFP: More bug fixes in the code

Where we overload the notation $\toIDesc{\V{TID}}$ to denote the
indexed description computed from the tagged indexed description
$\V{TID}$.

The type of $\F{eval}$ is strikingly similar to a
catamorphism. Indeed, implementing a single step of evaluation -- the
algebra -- is sufficient, as $\F{cataI}$ \note{We have not defined
  \F{cataI}!} gives, for free, the full evaluator. The implementation
is as follows:

@@

In this section, we develop more structure for our indexed
data-types. In Section~\ref{sec:desc-free-monad}, we have built a free
monad operation for simple descriptions. Building on this experience,
we are going to present its equivalent in the indexed world. The
process is the same. Namely, given an indexed functor, we derive the
indexed functor coding its free monad: \note{pwm: Whoa there. Maybe we
  should say something about IMonads in general before we get to this
  point?}

@@

In Section~\ref{sec:idesc-examples}, we had the intuition that our
datatypes $\HExprD$ and $\HExprVarD{\V{dom}}$ enjoy a monadic structure. We had
identified the variable substitution operation as the \bind\ of a free
monad. The definition of $\substI$ above confirms our intuition: using
$\substI$, we should easily obtain $\substH$. To do so, we first have
to massage the definition of our data-type, to exhibit its monadic
structure.

@@

The evaluator for closed terms we implemented in
Section~\ref{sec:idesc-examples} remains unchanged. It reduces closed
terms in $\FreeIMonad{\HExprFreeD}{\Ty}{\Val{}}\: \V{ty}$ to values in
$\Val{\V{ty}}$. We are therefore left with implementing $\substH$. We
simply have to fill in the right arguments to $\substI$, the type
guiding us:

>>>>

The type of $\F{eval}$ is strikingly similar to a
catamorphism. Indeed, implementing a single step of evaluation -- the
algebra -- is sufficient, as $\F{cataI}$ \note{We have not defined
  \F{cataI}!} gives, for free, the full evaluator. The implementation
is as follow:

@@

In this section, we develop more structure for our indexed
data-types. In Section~\ref{sec:desc-free-monad}, we have built a free
monad operation for simple descriptions. Building on this experience,
we are going to present its equivalent in the indexed world. The
process the same. Namely, given an indexed functor, we derive the
indexed functor coding its free monad: \note{pwm: Whoa there. Maybe we
  should say something about IMonads in general before we get to this
  point?}

@@

In Section~\ref{sec:idesc-examples}, we had the intuition that our
datatypes $\HExprD$ and $\HExprVarD{\V{dom}}$ enjoy a monadic structure. We had
identified the variable substitution operation as the \bind\ of a free
monad. The definition of $\substI$ above confirm our intuition: using
$\substI$, we should easily obtain $\substH$. To do so, we first have
to massage the definition of our data-type, to exhibit its monadic
structure.

@@

The evaluator for closed term we implemented in
Section~\ref{sec:idesc-examples} remains unchanged. It reduces closed
terms in $\FreeIMonad{\HExprFreeD}{\Ty}{\Val{}}\: \V{ty}$ to values in
$\Val{\V{ty}}$. We are therefore left with implementing $\substH$. We
simply have to fill in the right arguments to $\substI$, the type
guiding us:
